---
title: "DGM-RSN10"
author: "Simon Schwab"
date: "25 Sep 2017"
output:
  html_notebook: default
---

## Install required packages 
```{r}
# install.packages("multdyn")
# install.packages("testit")
# install.packages("ggplot2")
# install.packages("cowplot")
# install.packages("reshape2")
# install.packages("data.table")
```

## Load libraries 
```{r}

library(multdyn)
library(ggplot2)
library(cowplot)
library(reshape2)
library(data.table)
library(testthat)
library(testit)
```

## Main variables 
```{r}
PATH_HOME = "/home/simon"
PATH_NET  = file.path(PATH_HOME, 'Drive', 'MDM_NetMats10_results')
PATH_TS   = file.path(PATH_HOME, 'Drive', 'HCP900_Parcellation_Timeseries_Netmats_ICAd25')
PATH      = file.path(PATH_HOME, 'Dropbox', 'Data', 'DGM')
PATH_DATA = file.path(PATH, 'data')
PATH_DEMOG = file.path(PATH_HOME, 'Drive', 'HCP')
PATH_FIG  = file.path(PATH, 'figures')

N      = 500
N_comp = 10 # RSNs
N_t    = 1200 # Volumes
N_runs = 4
INFO   = 'NetMats10'
SUBJECTS = as.matrix(read.table(file.path(PATH_TS, 'subjectIDs.txt')))
TR=0.72
labels = read.table(file.path(PATH, 'results', 'Net10Labels.txt'), header = T)
labels = labels[order(labels$NoNetMats25),]
COMP=labels$NoNetMats25

print(labels)
```

## Demographics
We use the HCP 900 release

Load data
```{r}
subj = as.matrix(read.table(file.path(PATH_TS, 'subjectIDs.txt')))
subj=subj[1:N]
           
demog=read.table(file.path(PATH_DEMOG, 'unrestricted_schwab_9_19_2017_8_41_11.csv'), 
                 sep = ",", header = TRUE)
idx = is.element(demog$Subject, subj)
assert(sum(idx) == N)

demog = subset(demog, idx)
assert(nrow(demog) == N)
```

```{r}
summary(demog$Gender)/N

summary(demog$Age)/N
```

## Loading network data
```{r}
# subj_r1 = vector(mode = "list", length = N)
# subj_r2 = vector(mode = "list", length = N)
# subj_r3 = vector(mode = "list", length = N)
# subj_r4 = vector(mode = "list", length = N)
# 
# for (s in 1:N) {
#   subj_r1[[s]] = read.subject(PATH_NET, sprintf("%s_Run_%03d", SUBJECTS[s], 1), N_comp)
#   subj_r2[[s]] = read.subject(PATH_NET, sprintf("%s_Run_%03d", SUBJECTS[s], 2), N_comp)
#   subj_r3[[s]] = read.subject(PATH_NET, sprintf("%s_Run_%03d", SUBJECTS[s], 3), N_comp)
#   subj_r4[[s]] = read.subject(PATH_NET, sprintf("%s_Run_%03d", SUBJECTS[s], 4), N_comp)
#   print(sprintf("Subject %03d loaded",s))
# }
# 
# mdm.net10.r1 = mdm.group(subj_r1)
# mdm.net10.r2 = mdm.group(subj_r2)
# mdm.net10.r3 = mdm.group(subj_r3)
# mdm.net10.r4 = mdm.group(subj_r4)
# 
# # save some space
# mdm.net10.r1$models = NULL
# mdm.net10.r2$models = NULL
# mdm.net10.r3$models = NULL
# mdm.net10.r4$models = NULL
# 
# f=file(file.path(PATH_DATA,"net10.RData"))
# save(mdm.net10.r1, mdm.net10.r2, mdm.net10.r3, mdm.net10.r4, file = f, compress = T)
# close(f)
load(file.path(PATH, 'results', 'net10.RData'))
```

## Plot: discount factor delta distribution per node
```{r, fig.height=4, fig.width=5}

d.r1=melt(mdm.net10.r1$df_)
d.r2=melt(mdm.net10.r2$df_)
d.r3=melt(mdm.net10.r3$df_)
d.r4=melt(mdm.net10.r4$df_)


p1 = ggplot(d.r1, aes(x=as.factor(Var2), y=value)) +
  geom_point(shape=1, color="gray50", size=2, position = position_jitter(width = NULL, height = 0.01)) +
  geom_boxplot(width=0.6) +
  ggtitle(sprintf("Run 1", N)) + ylab("df") + xlab("node")

p2 = ggplot(d.r2, aes(x=as.factor(Var2), y=value)) +
  geom_point(shape=1, color="gray50", size=2, position = position_jitter(width = NULL, height = 0.01)) +
  geom_boxplot(width=0.6) +
  ggtitle(sprintf("Run 2", N)) + ylab("df") + xlab("node")

p3 = ggplot(d.r3, aes(x=as.factor(Var2), y=value)) +
  geom_point(shape=1, color="gray50", size=2, position = position_jitter(width = NULL, height = 0.01)) +
  geom_boxplot(width=0.6) +
  ggtitle(sprintf("Run 3", N)) + ylab("df") + xlab("node")

p4 = ggplot(d.r4, aes(x=as.factor(Var2), y=value)) +
  geom_point(shape=1, color="gray50", size=2, position = position_jitter(width = NULL, height = 0.01)) +
  geom_boxplot(width=0.6) +
  ggtitle(sprintf("Run 4", N)) + ylab("df") + xlab("node")

plot_grid(p1, p2, p3, p4, ncol = 2, nrow = 2)
```

## Load time series data
```{r}
# f = list.files(file.path(PATH_TS, "node_timeseries", "3T_HCP820_MSMAll_d25_ts2"), "*.txt")
# # read data
# ts = array(NA, dim=c(N_t, N_comp, N_runs, N))
# for (s in 1:N) {
#   d = scaleTs(as.matrix(read.table(file.path(PATH_TS, "node_timeseries", "3T_HCP820_MSMAll_d25_ts2", f[s]))))
#   assert(nrow(d) == N_t*N_runs)
#   ts[,,1,s] = d[1:1200,COMP]
#   ts[,,2,s] = d[1201:2400,COMP]
#   ts[,,3,s] = d[2401:3600,COMP]
#   ts[,,4,s] = d[3601:4800,COMP]
# }
# 
# f=file(file.path(PATH,"ts10.RData"))
# save(ts, file = f)
# close(f)
load(file.path(PATH, 'results', 'ts10.RData'))
```

### Variance of nodes
We calculate the SD across time for the subject's node.
```{r}
# ts 1200 x 10 x 4 x 500
r1=apply(ts[,,1,], c(3,2), sd)
r2=apply(ts[,,2,], c(3,2), sd)
r3=apply(ts[,,3,], c(3,2), sd)
r4=apply(ts[,,4,], c(3,2), sd)
```

```{r, fig.height=4, fig.width=6}
p1 = ggplot(melt(r1), aes(x=as.factor(Var2), y=value)) +
  geom_point(shape=1, color="gray50", size=2, position = position_jitter(width = NULL, height = 0.01)) +
  geom_boxplot(width=0.3) +
  ggtitle(sprintf("Run 1", N)) + ylab("SD") + xlab("RSNs")

p2 = ggplot(melt(r2), aes(x=as.factor(Var2), y=value)) +
  geom_point(shape=1, color="gray50", size=2, position = position_jitter(width = NULL, height = 0.01)) +
  geom_boxplot(width=0.3) +
  ggtitle(sprintf("Run 2", N)) + ylab("SD") + xlab("RSNs")

p3 = ggplot(melt(r3), aes(x=as.factor(Var2), y=value)) +
  geom_point(shape=1, color="gray50", size=2, position = position_jitter(width = NULL, height = 0.01)) +
  geom_boxplot(width=0.3) +
  ggtitle(sprintf("Run 3", N)) + ylab("SD") + xlab("RSNs")

p4 = ggplot(melt(r4), aes(x=as.factor(Var2), y=value)) +
  geom_point(shape=1, color="gray50", size=2, position = position_jitter(width = NULL, height = 0.01)) +
  geom_boxplot(width=0.3) +
  ggtitle(sprintf("Run 4", N)) + ylab("SD") + xlab("RSNs")

plot_grid(p1, p2, p3, p4, ncol = 2, nrow = 2)
ggsave(path = PATH_FIG, "Sd_10RSNs.png")
```

## Correlation Plots
```{r, fig.height=4.7, fig.width=6.5, message=FALSE}
LIM=c(-0.65,0.65)

p1 = gplotMat(rmdiag(corTs(ts[,,1,])), title=sprintf("Run 1", N), lim=LIM, nodeLabels = labels$Label,
              axisTextSize = 8, xAngle = 90, colMapLabel=expression("Pearson\'s"~italic(r)),
              gradient = c("blue", "white", "red")) +
  xlab("Node") + ylab("Node") + scale_x_continuous(breaks = 0.5:9.5, labels = labels$Label )

p2 = gplotMat(rmdiag(corTs(ts[,,2,])), title=sprintf("Run 2", N), lim=LIM, nodeLabels = labels$Label,
              axisTextSize = 8, xAngle = 90, colMapLabel=expression("Pearson\'s"~italic(r)),
              gradient = c("blue", "white", "red")) +
  xlab("Node") + ylab("Node") + scale_x_continuous(breaks = 0.5:9.5, labels = labels$Label )

p3 = gplotMat(rmdiag(corTs(ts[,,3,])), title=sprintf("Run 3", N), lim=LIM, nodeLabels = labels$Label,
              axisTextSize = 8, xAngle = 90, colMapLabel=expression("Pearson\'s"~italic(r)),
              gradient = c("blue", "white", "red")) +
  xlab("Node") + ylab("Node") + scale_x_continuous(breaks = 0.5:9.5, labels = labels$Label )

p4 = gplotMat(rmdiag(corTs(ts[,,4,])), title=sprintf("Run 4", N), lim=LIM, nodeLabels = labels$Label,
              axisTextSize = 8, xAngle = 90, colMapLabel=expression("Pearson\'s"~italic(r)),
              gradient = c("blue", "white", "red")) +
  xlab("Node") + ylab("Node") + scale_x_continuous(breaks = 0.5:9.5, labels = labels$Label )

plot_grid(p1, p2, p3, p4, ncol = 2, nrow = 2, rel_widths = c(1, 1))
```

## Plot example timeseries
```{r, fig.height=8, fig.width=10}
idx = 1:round(120/TR) # first 2 minutes

# random sampling of subject s and nodes n
nodes = 5 # no. of nodes to plot

d = ts[idx,sample(N_comp,nodes),,sample(N,1)]

p1 = ggplot(melt(d[,1,]), aes(x = Var1, y = value, group=Var2, color=as.factor(Var2))) + 
  geom_line() + theme_minimal() + ggtitle("Run 1")

p2 = ggplot(melt(d[,2,]), aes(x = Var1, y = value, group=Var2, color=as.factor(Var2))) +
  geom_line() + theme_minimal() + ggtitle("Run 2")

p3 = ggplot(melt(d[,3,]), aes(x = Var1, y = value, group=Var2, color=as.factor(Var2))) +
  geom_line() + theme_minimal() + ggtitle("Run 3")

p4 = ggplot(melt(d[,4,]), aes(x = Var1, y = value, group=Var2, color=as.factor(Var2))) + 
  geom_line() + theme_minimal() + ggtitle("Run 4")

plot_grid(p1, p2, p3, p4, ncol = 1, nrow = 4, rel_widths = c(1, 1))
```

## Network consistency across subjects
```{r}
stats.r1 = binom.nettest(mdm.net10.r1$am, alter = "greater")
stats.r2 = binom.nettest(mdm.net10.r2$am, alter = "greater")
stats.r3 = binom.nettest(mdm.net10.r3$am, alter = "greater")
stats.r4 = binom.nettest(mdm.net10.r4$am, alter = "greater")
```

### Difference between e=0 and e=20
```{r}
x = c(sum(mdm.net10.r1$tam != mdm.net10.r1$am),
      sum(mdm.net10.r2$tam != mdm.net10.r2$am),
      sum(mdm.net10.r3$tam != mdm.net10.r3$am),
      sum(mdm.net10.r4$tam != mdm.net10.r4$am)
)
print(x)
print(x/(N*N_comp*(N_comp-1)))

```


## Figure 5
```{r, fig.width=5.8, fig.height=9.8, message=FALSE}
mylim = c(0, 0.68)
pos = 0.5:9.5
s = 0.2
p1 = gplotMat(stats.r1$adj, title = "Run 1", nodeLabels=labels$Label,
              axisTextSize=9, xAngle=90, lim = mylim) +
  scale_x_continuous(breaks = pos, labels = labels$Label) +
  theme(plot.margin = unit(c(s, 0, 0, 0), "cm"))

p2 = gplotMat(rmna(stats.r1$adj_fdr), title = "binomial test",
              nodeLabels=labels$Label, axisTextSize=9, xAngle=90, lim = mylim) +
  scale_x_continuous(breaks = pos, labels = labels$Label ) +
  theme(plot.margin = unit(c(s, 0, 0, 0), "cm"))

p3 = gplotMat(stats.r2$adj, title = "Run 2", nodeLabels=labels$Label,
              axisTextSize=9, xAngle=90, lim = mylim) +
  scale_x_continuous(breaks = pos, labels = labels$Label) +
  theme(plot.margin = unit(c(s, 0, 0, 0), "cm"))

p4 = gplotMat(rmna(stats.r2$adj_fdr), title = "binomial test",
              nodeLabels=labels$Label, axisTextSize=9, xAngle=90, lim = mylim) +
  scale_x_continuous(breaks = pos, labels = labels$Label) +
  theme(plot.margin = unit(c(s, 0, 0, 0), "cm"))

p5 = gplotMat(stats.r3$adj, title = "Run 3", nodeLabels=labels$Label,
              axisTextSize=9, xAngle=90, lim = mylim) +
  scale_x_continuous(breaks = pos, labels = labels$Label) +
  theme(plot.margin = unit(c(s, 0, 0, 0), "cm"))

p6 = gplotMat(rmna(stats.r3$adj_fdr), title = "binomial test",
              nodeLabels=labels$Label, axisTextSize=9, xAngle=90, lim = mylim) +
  scale_x_continuous(breaks = pos, labels = labels$Label) +
  theme(plot.margin = unit(c(s, 0, 0, 0), "cm"))

p7 = gplotMat(stats.r4$adj, title = "Run 4", nodeLabels=labels$Label,
              axisTextSize=9, xAngle=90, lim = mylim) +
  scale_x_continuous(breaks = pos, labels = labels$Label) +
  theme(plot.margin = unit(c(s, 0, 0, 0), "cm"))

p8 = gplotMat(rmna(stats.r4$adj_fdr), title = "binomial test",
              nodeLabels=labels$Label, axisTextSize=9, xAngle=90, lim = mylim) +
  scale_x_continuous(breaks = pos, labels = labels$Label) +
  theme(plot.margin = unit(c(s, 0, 0, 0), "cm"))

plot_grid(p1, p2, p3, p4, p5, p6, p7, p8, ncol = 2, nrow = 4, rel_heights = c(1,1,1,1))
ggsave(path = PATH_FIG, "Fig5.png")
```

## Networks consistency across runs
```{r}
# edge reproduced in 3 runs or more
m3 = mdm.net10.r1$am + mdm.net10.r2$am + mdm.net10.r3$am + mdm.net10.r4$am > 2
# edge reproduced in all runs
m4 = mdm.net10.r1$am * mdm.net10.r2$am * mdm.net10.r3$am * mdm.net10.r4$am
# consistently no edge in all runs
mn = (1-mdm.net10.r1$am) * (1-mdm.net10.r2$am) * (1-mdm.net10.r3$am) * (1-mdm.net10.r4$am)

stats.m3 = binom.nettest(m3, alter = "greater")
stats.m4 = binom.nettest(m4, alter = "greater")
stats.mn = binom.nettest(mn, alter = "greater")
```

## Figure 6
```{r, fig.height=7.8, fig.width=6.2}
p1 = gplotMat(stats.m3$adj, title = "edge in 3/4 runs", nodeLabels=labels$Label,
              axisTextSize=9, xAngle=90, lim = c(0, 0.6)) +
  scale_x_continuous(breaks = pos, labels = labels$Label)

p2 = gplotMat(rmna(stats.m3$adj_fdr), title = "binomial test",
              nodeLabels=labels$Label, axisTextSize=9, xAngle=90, lim = c(0, 0.6)) +
  scale_x_continuous(breaks = pos, labels = labels$Label)

p3 = gplotMat(stats.m4$adj, title = "edge in 4/4 runs", nodeLabels=labels$Label,
              axisTextSize=9, xAngle=90, lim = c(0, 0.32)) +
  scale_x_continuous(breaks = pos, labels = labels$Label)

p4 = gplotMat(rmna(stats.m4$adj_fdr), title = "binomial test",
              nodeLabels=labels$Label, axisTextSize=9, xAngle=90, lim = c(0,0.32)) +
  scale_x_continuous(breaks = pos, labels = labels$Label)

p5 = gplotMat(rmdiag(stats.mn$adj), title = "no edge in 4/4 runs", nodeLabels=labels$Label,
              gradient = c("white", "violet", "blue"),
              axisTextSize=9, xAngle=90) +
  scale_x_continuous(breaks = pos, labels = labels$Label)

p6 = gplotMat(rmdiag(rmna(stats.mn$adj_fdr)), title = "binomial test",
              gradient = c("white", "violet", "blue"),
              nodeLabels=labels$Label, axisTextSize=9, xAngle=90) +
  scale_x_continuous(breaks = pos, labels = labels$Label)

plot_grid(p1, p2, p3, p4, p5, p6, labels=c("A", "", "", "", "B", ""),
          ncol = 2, nrow = 3, rel_heights = c(1,1,1))

ggsave(path = PATH_FIG, "Fig6.png")
```

```{r Clustering, eval=FALSE, include=FALSE}
# distance
# d1 = dist(t(array(mdm.net10.r1$am, dim = c(N_comp*N_comp,N))), method = "binary")
# d2 = dist(t(array(mdm.net10.r2$am, dim = c(N_comp*N_comp,N))), method = "binary")
# d3 = dist(t(array(mdm.net10.r3$am, dim = c(N_comp*N_comp,N))), method = "binary")
# d4 = dist(t(array(mdm.net10.r4$am, dim = c(N_comp*N_comp,N))), method = "binary")

d1 = dist(t(array(rmna(mdm.net10.r1$lpl), dim = c(N_comp*N_comp,N))))
d2 = dist(t(array(rmna(mdm.net10.r2$lpl), dim = c(N_comp*N_comp,N))))
d3 = dist(t(array(rmna(mdm.net10.r3$lpl), dim = c(N_comp*N_comp,N))))
d4 = dist(t(array(rmna(mdm.net10.r4$lpl), dim = c(N_comp*N_comp,N))))

X=array(NA, dim=c(10,10,2000))
X[,,1:500]=mdm.net10.r1$lpl
X[,,501:1000]=mdm.net10.r2$lpl
X[,,1001:1500]=mdm.net10.r3$lpl
X[,,1501:2000]=mdm.net10.r4$lpl

am=array(NA, dim=c(10,10,2000))
am[,,1:500]=mdm.net10.r1$am
am[,,501:1000]=mdm.net10.r2$am
am[,,1001:1500]=mdm.net10.r3$am
am[,,1501:2000]=mdm.net10.r4$am

d1 = dist(t(array(rmna(X), dim = c(N_comp*N_comp,N*4))))

clust1 = hclust(d1, method = "complete")

clust1 = hclust(d1, method = "complete")
clust2 = hclust(d2, method = "complete")
clust3 = hclust(d3, method = "complete")
clust4 = hclust(d4, method = "complete")

K=5
grp1 = cutree(clust1, k = K)
grp2 = cutree(clust2, k = K)
grp3 = cutree(clust3, k = K)
grp4 = cutree(clust4, k = K)

rbind(summary(as.factor(grp1)), summary(as.factor(grp2)), summary(as.factor(grp3)), summary(as.factor(grp4)))
```

```{r Clustering: Plot, eval=FALSE, fig.height=5, fig.width=7, include=FALSE}
par(mfrow=c(2,2))
plot(clust1)
plot(clust2)
plot(clust3)
plot(clust4)
```

```{r Plot Clusters, eval=FALSE, fig.height=7, fig.width=8, include=FALSE}
S = array(NaN, dim=c(N_comp,N_comp,K))
grp3[1]=5
for (i in 1:K){
  S[,,1,i]=binom.nettest(mdm.net10.r1$am[,,grp1==i], alter = "greater")$adj_fdr
  S[,,2,i]=binom.nettest(mdm.net10.r2$am[,,grp2==i], alter = "greater")$adj_fdr
  S[,,3,i]=binom.nettest(mdm.net10.r3$am[,,grp3==i], alter = "greater")$adj_fdr
  S[,,4,i]=binom.nettest(mdm.net10.r4$am[,,grp4==i], alter = "greater")$adj_fdr
}

for (i in 1:K){
  S[,,i]=binom.nettest(am[,,grp1==i], alter = "greater")$adj_fdr
  #S[,,i]=binom.nettest(am[,,grp2==i], alter = "greater")$adj_fdr
  #S[,,i]=binom.nettest(am[,,grp3==i], alter = "greater")$adj_fdr
  #S[,,i]=binom.nettest(am[,,grp4==i], alter = "greater")$adj_fdr
}

# run 1
p11 = gplotMat(rmna(S[,,1]), hasColMap = F, axisTextSize = 9)
p12 = gplotMat(rmna(S[,,2]), hasColMap = F, axisTextSize = 9)
p13 = gplotMat(rmna(S[,,3]), hasColMap = F, axisTextSize = 9)
p14 = gplotMat(rmna(S[,,4]), hasColMap = F, axisTextSize = 9)
p15 = gplotMat(rmna(S[,,5]), hasColMap = F, axisTextSize = 9)

# run 2
p21 = gplotMat(rmna(S[,,2,1]), hasColMap = F, axisTextSize = 9)
p22 = gplotMat(rmna(S[,,2,2]), hasColMap = F, axisTextSize = 9)
p23 = gplotMat(rmna(S[,,2,3]), hasColMap = F, axisTextSize = 9)
p24 = gplotMat(rmna(S[,,2,4]), hasColMap = F, axisTextSize = 9)
p25 = gplotMat(rmna(S[,,2,5]), hasColMap = F, axisTextSize = 9)

# run 3
p31 = gplotMat(rmna(S[,,3,1]), hasColMap = F, axisTextSize = 9)
p32 = gplotMat(rmna(S[,,3,2]), hasColMap = F, axisTextSize = 9)
p33 = gplotMat(rmna(S[,,3,3]), hasColMap = F, axisTextSize = 9)
p34 = gplotMat(rmna(S[,,3,4]), hasColMap = F, axisTextSize = 9)
p35 = gplotMat(rmna(S[,,3,5]), hasColMap = F, axisTextSize = 9)

# run 4
p41 = gplotMat(rmna(S[,,4,1]), hasColMap = F, axisTextSize = 9)
p42 = gplotMat(rmna(S[,,4,2]), hasColMap = F, axisTextSize = 9)
p43 = gplotMat(rmna(S[,,4,3]), hasColMap = F, axisTextSize = 9)
p44 = gplotMat(rmna(S[,,4,4]), hasColMap = F, axisTextSize = 9)
p45 = gplotMat(rmna(S[,,4,5]), hasColMap = F, axisTextSize = 9)

plot_grid(p11,p12,p13,p14,p15,p21,p22,p23,p24,p25,
          p31,p32,p33,p34,p35,p41,p42,p43,p44,p45, nrow = 4, ncol = 5)

plot_grid(p11,p12,p13,p14,p15, nrow = 2, ncol = 3)

#ggsave(path = '/home/simon', "Fig.png")

```

